---
title: "R Novice Inflammation data analysyz"
author: "Brin"
date: "2 November 2016"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
```

```{r data}
data("mtcars")
mtcars
anumber <- 42
```


#a bullet list
- bullet 1
- bullet fucking 2
- bullet likes it's cool

#n italicised word
_Italy_ or *Greece*

#a bolded word
__United States__ or **Another bold country**

# has each type of header (1,2,3)
## each type
### of header

#a number computed inline from R
```{r}
2+2
```


# a table showing the means of a variable grouped on a different variable
```{r}
mtcars %>% group_by(cyl) %>% summarise(mpg_means = mean(mpg)) %>% View()
```

```{r bitshewants, warning=FALSE, echo=TRUE}
# and R code block that is shown in the output that creates a dot plot
plot(c(1:100),c(1:100))

# an R code black that is shown and that creates a boxplot for each group
mtcars %>% group_by(cyl) %>% summarise(mpg_means = mean(mpg)) %>% ggplot(aes(x = mpg_means, y = hp, group = cyl)) + geom_boxplot()

# an R code bloack that isn't shown and that creates a histogram
```

```{r doit, warning=FALSE, include=FALSE, echo=FALSE}
magic <- c("Monkey", "Dog", "Fish", "Zebra", "Cat", "Long horse", "Cantaloupe", "Tiger", "Beetle", "Leopard", "Snail", "Chihuahua", "Yes")
loadPtData <- function(datadir,datapattern, printall, makepdf, domagic)
{
  if(makepdf) pdf(paste0("Report ",Sys.Date(),".pdf"))
  i <- 0
  filenames = list.files(path=datadir,pattern=datapattern,full.names=TRUE)
  for(ptfile in filenames) 
  {
    i <- i + 1
    ptid <- as.numeric(regmatches(ptfile, regexpr("[0-9].*[0-9]", ptfile)))
    print(as.numeric(ptid))
    if(domagic) ptid <- rownames(mtcars)[ptid]
    print(paste("Looking at",ptfile))
    ptdata <- read.csv(paste(getwd(),ptfile, sep = "/"), header = FALSE)
    par(mfrow=c(2,3))
    plot(apply(ptdata,2,mean), main=paste("Patient",ptid), ylab="Mean inflammations", pch="$", asp=1)
    if(printall)
    {
      plot(apply(ptdata,2,min), main=paste("Patient",ptid), ylab="Minimum inflammations", pch="@", asp=1)
      plot(apply(ptdata,2,max), main=paste("Patient",ptid), ylab="Maximum inflammations", pch="&", asp=1)
    }
  }
  if(makepdf) dev.off()
  #if(printall & !makepdf & domagic) summary(read.FCS("C:/Users/Brin/Desktop/Uni/2016/Experiments/BMR1611 - ILC sorting pilot 7/161030 1611 ILC sort pilot 7 Fortessa/1611_1 neg MACS_013.fcs"))
}
```

HI SAMMMMMMMMMMM

```{r main, warning=FALSE}
loadPtData("data","inflammation.*csv", TRUE, FALSE, TRUE)